Tropical Andes plant occurrence data GBIF

### 2023-09-19 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
remove forest subset code
clean up unnecessary code

# Load required packages
```{r}
library(dplyr)
library(rgbif) 
```

# Plant occurrences using IUCN habitat subset
## Read in IUCN data
Data was obtained from https://www.iucnredlist.org/search?permalink=9621ab77-2341-4bf8-9557-b7f19f7f2a35
```{r}
plants_habitats <- read.csv(file.path(data_path,"IUCN/Tropical Andes Plants - Search Results/habitats.csv"))
```

## Create species list from IUCN data
```{r}
plant_species <- unique(plants_habitats$scientificName)
print("The number of species on the IUCN is")
length(plant_species)
```

## Match species names to GBIF
```{r}
gbif_taxon_keys <- plant_species %>% 
name_backbone_checklist() %>% # match to backbone 
filter(!matchType == "NONE") %>% # get matched names
pull(usageKey) 
```

## Download data
```{r}
occ_download(
pred_in("taxonKey", gbif_taxon_keys),
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0097296-230530130749713", path = output_path) %>%
  occ_download_import()
```

## Summary 
```{r}
glimpse(d)
```

```{r}
print("The number of occurrences is")
nrow(d)
print("The number of species is" )
length(unique(d$species))
print("The number of families is" )
length(unique(d$family))
```

# Plant occurrences without habitat subset

## Download data
```{r}
occ_download(
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d2 <- occ_download_get("0097297-230530130749713", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

## Summary 
```{r}
glimpse(d2)
```

```{r}
print("The number of occurrences is")
nrow(d2)
print("The number of species is" )
length(unique(d2$species))
print("The number of families is" )
length(unique(d2$family))
```

# Extract species list
```{r}
GBIF_SpeciesList <- unique(d2$species)
```

>>>>

# Load required packages
```{r}
library(dplyr)
library(rgbif)
library(raster)
library(sf)
```

# Download plant occurrence data from GBIF
```{r}
occ_download(
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0097297-230530130749713", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

# Summary 
```{r}
glimpse(d1)
```

```{r}
print("The number of occurrences is")
nrow(d1)
print("The number of species is" )
length(unique(d1$species))
print("The number of families is" )
length(unique(d1$family))
```

# Extract species list
```{r}
GBIF_SpeciesList <- unique(d1$species)
```
